---
title: "Indoor-Location-and-Navigation"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

goal: predict the floor and waypoint (x, y) at provided timestamps

```{r}
# init 
rm(list = ls())

# load packages
library(tidyverse)
library(magrittr)
library(png)
library(rjson)
library(viridis)
library(gridExtra)

# directories
dirs <- list(
  train = './data/train/',
  test = './data/test/',
  metadata = './data/metadata/'
)

```

```{r}
parse_file <- function(file_path, type = 'train') {
  print(str_c(' > parsing', file_path, '... '))
  
  # get meta data
  meta_data <- read_lines(file_path, n_max = 10)
  path_vec <- str_split(file_path, '/', simplify = T)
  
  # getting site_id from file header, because that's how it is stored in the test set
  site_id <- meta_data[str_detect(meta_data, 'SiteID:')] %>%
    str_extract(., '^#\\tSiteID\\:(\\w+)') %>%
    str_sub(., str_locate(., ":")[1]+1, -1)
  
  if(type == 'train') {
    meta <- list(
      type = path_vec[3],
      floor_id = path_vec[6],
      site_id = site_id,
      file_id = path_vec[7]
    )
  } else {
    meta <- list(
      type = path_vec[3],
      floor_id = NULL,
      site_id = site_id,
      file_id = path_vec[4]
    )
  }
  
  # get the trace data 
  type_2_col_names <- list(
    "TYPE_WAYPOINT" = list(n_cols = 3, col_names = c('wy_x','wy_y'), chr_cols = NULL),
    "TYPE_GYROSCOPE" = list(n_cols = 5, col_names = c('tg_x','tg_y','tg_z','tg_a'), chr_cols = NULL),
    "TYPE_ACCELEROMETER" = list(n_cols = 5, col_names = c('acc_x','acc_y','acc_z','acc_a'), chr_cols = NULL),
    "TYPE_MAGNETIC_FIELD" = list(n_cols = 5, col_names = c('mf_x','mf_y','mf_z','mf_a'), chr_cols = NULL),
    "TYPE_ROTATION_VECTOR" = list(n_cols = 5, col_names = c('rv_x','rv_y','rv_z','rv_a'), chr_cols = NULL),
    "TYPE_ACCELEROMETER_UNCALIBRATED" = list(n_cols = 8, col_names = c('accu_x','accu_y','accu_z','accu_x2','accu_y2','accu_z2','accu_a'), chr_cols = NULL),
    "TYPE_GYROSCOPE_UNCALIBRATED" = list(n_cols = 8, col_names = c('gyru_x','gyru_y','gyru_z','gyru_x2','gyru_y2','gyru_z2','gyru_a'), chr_cols = NULL),
    "TYPE_MAGNETIC_FIELD_UNCALIBRATED" = list(n_cols = 8, col_names = c('mfu_x','mfu_y','mfu_z','mfu_x2','mfu_y2','mfu_z2','mfu_a'), chr_cols = NULL),
    "TYPE_WIFI" = list(n_cols = 6, col_names = c('wf_ssid','wf_bssid','wf_rssi','wf_freq','wf_lst'), chr_cols = c('wf_ssid','wf_bssid'))
  )
  
  process_type_data <- function(type_name, df) {
    df_type <- df[, 1:type_2_col_names[[type_name]]$n_cols]
    names(df_type) <- c('id', type_2_col_names[[type_name]]$col_names)
    
    if(is.null(type_2_col_names[[type_name]]$chr_cols)) {
      # change all columns to numeric
      df_type %<>%
        mutate_all(as.numeric)
    } else {
      # change all to numeric except chr_cols
      num_cols <- type_2_col_names[[type_name]]$col_names[!(type_2_col_names[[type_name]]$col_names %in% type_2_col_names[[type_name]]$chr_cols)]
      df_type %<>%
        mutate_at(num_cols, as.numeric)
    }
    
    return(df_type)
  }
  
  get_type <- function(df, type_name) {
    return(df %>% filter(V2 == type_name) %>% unnest(c(data)) %>% ungroup %>% select(-V2))
  }

  df <- read.csv2(file_path, sep="\t", skip=0, stringsAsFactors = FALSE, comment.char = "#", 
                header=FALSE, col.names = paste0("V", seq_len(9)))

  df_ty <- df %>%
    group_by(V2) %>%
    nest() %>%
    filter(V2 %in% names(type_2_col_names)) %>%
    transmute(V2, data = map2(.x = V2, .y = data, ~process_type_data(.x , .y)))
  
  # way points
  wp <- get_type(df_ty, 'TYPE_WAYPOINT')
  
  # wifi data
  wifi <- get_type(df_ty, 'TYPE_WIFI')
  
  # device
  dd <- get_type(df_ty, 'TYPE_GYROSCOPE') %>%
    inner_join(get_type(df_ty, 'TYPE_ACCELEROMETER'), by='id') %>%
    inner_join(get_type(df_ty, 'TYPE_MAGNETIC_FIELD'), by='id') %>%
    inner_join(get_type(df_ty, 'TYPE_ROTATION_VECTOR'), by='id') %>%
    mutate(idsec = round(id/1000))
  
  return(list(
    meta = meta,
    wp = wp,
    device = dd, 
    wifi = wifi
  ))
  
}

tr_files <- list.files(path = dirs$train, recursive = TRUE, pattern = "\\.txt$", full.names = TRUE)
```

```{r, fig.width=15, fig.height=25}
# visualize paths
draw_traces_on_floor <- function(traces, site_id, floor_id, n_paths) {
  img <- readPNG(paste0(dirs$metadata, site_id, "/", floor_id, "/floor_image.png"))
  floor_info <- fromJSON(file = paste0(dirs$metadata, site_id, "/", floor_id, '/floor_info.json'))
  
  floor_image <- list(
    width  = dim(img)[1],
    height = dim(img)[2])
  
  floor_image$ratio_x <- floor_image$width/floor_info$map_info$width
  floor_image$ratio_y <- floor_image$height/floor_info$map_info$height
  
  trs <- tr_files[str_detect(tr_files, site_id) & str_detect(tr_files, floor_id)] 
  n_max <- length(trs)
  
  if(n_paths > n_max | n_paths == -1) {
    n_paths <- n_max
  }
  
  trs %<>%
    sample(., n_paths) %>%
    enframe() %>%
    mutate(wps = map(.x = value, ~parse_file(.x)$wp))
    
  trs_u <- trs %>%
    select(-value) %>%
    unnest(cols = c(wps)) %>%
    arrange(name, id) %>%
    mutate(x = wy_x * floor_image$ratio_x,
           y = wy_y * floor_image$ratio_y)
  
  p <- trs_u %>%
    ggplot() +
    annotation_raster(img, xmin = 0, xmax = floor_image$width, ymin = 0, ymax = floor_image$height) +
    # geom_point() +
    # geom_line() +
    geom_path(aes(x = x, y = y, colour = factor(name), group = factor(name))) +
    geom_point(aes(x = x, y = y, colour = factor(name), group = factor(name))) +
    scale_color_viridis(alpha = 1, begin = 0, end = 1, direction = 1, discrete = TRUE, option = "D") +
    theme_minimal() +
    theme(legend.position='none') +
    xlim(0, floor_image$width) +
    ylim(0, floor_image$height)
 
  return(p)
}

site_id <- '5a0546857ecc773753327266'
floor_vec <- c('B1', 'F1', 'F2', 'F3', 'F4')
n_paths <- 100
p <- list()

for(i in seq_along(floor_vec)) {
  p[[i]] <- draw_traces_on_floor(tr_files, site_id = site_id, floor_id = floor_vec[i], 100)
}

do.call(grid.arrange, c(p, ncol = 2))
```

??? :

* are test sites and floors in train set
* are the test traces in the train set as well
* how to connect waypoint data with sensors data ?


* relationships between each sensor data, as well as sensors and waypoints
** wifi
** smartphone sensors

* relationship between sensors, waypoints and floor number

```{r}
# checking what sites are in train and test sets
# and whether there is any overlap
te_files <- list.files(path = dirs$test, recursive = TRUE, pattern = "\\.txt$", full.names = TRUE)

df_tr <- tr_files %>%
  enframe(name = NULL) %>%
  mutate(path_chunks = str_split(value, '/')) %>%
  mutate(site_id = map_chr(path_chunks, 5),
         floor_id = map_chr(path_chunks, 6),
         path_id = map_chr(path_chunks, 7)) %>%
  mutate(path_id = str_trim(str_replace(path_id, '.txt', ''))) %>%
  select(-path_chunks, -value)

df_te <- te_files %>%
  enframe(name = NULL) %>%
  mutate(meta = map(.x = value, ~parse_file(.x, 'test')$meta)) %>%
  mutate(site_id = map_chr(meta, function(x) x$site_id),
         path_id = map_chr(meta, function(x) x$file_id)) %>%
  mutate(path_id = str_trim(str_replace(path_id, '.txt', ''))) %>%
  select(-meta, -value)

# takes long to genereate these, so I save them jic
# write.csv(df_tr, './temp/train_data_meta.csv', row.names = FALSE)
# write.csv(df_te, './temp/test_data_meta.csv', row.names = FALSE)

tr_sites_vec <- df_tr %>%
  select(site_id) %>%
  unique() %>%
  pull()

te_sites_vec <- df_te %>%
  select(site_id) %>%
  unique() %>%
  pull()
  
df_te %>%
  select(site_id) %>%
  unique() %>%
  mutate(is_in_tr = site_id %in% tr_sites_vec) %>%
  count(is_in_tr)
```

Training set: 204 sites
Test set: 24 sites
All test sites are in training set
None of the paths are in the test set





