---
title: "Indoor-Location-and-Navigation"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

goal: predict the floor and waypoint (x, y) at provided timestamps

```{r}
# init 
rm(list = ls()); invisible(gc())

# load packages
library(tidyverse)
library(magrittr)
library(png)
library(rjson)
library(viridis)
library(gridExtra)
library(lubridate)
library(plotly)

# directories
dirs <- list(
  train = './data/train/',
  test = './data/test/',
  metadata = './data/metadata/'
)
```

```{r}
# floor dictionary: https://www.kaggle.com/oxzplvifi/indoor-preprocessing-and-eda
floor_id_2_nr <- list(
  "B3"=-3,"B2"=-2,"B1"=-1,"F1"=0,"1F"=0,"F2"=1,"2F"=1,"F3"=2,"3F"=2,"F4"=3,"4F"=3, "F5"=4,"5F"=4,"F6"=5,"6F"=5,"F7"=6,"7F"=6,
  "F8"=7,"8F"= 7,"F9"=8,"9F"=8,"F10"=9, "B"=0,"BF"=1,"BM"=2, "G"=0, "M"=0, "P1"=0,"P2"=1, "LG2"=-2,"LG1"=-1,"LG"=0, "LM"=0,"L1"=1,"L2"=2, 
  "L3"=3,"L4"=4,"L5"=5,"L6"=6,"L7"=7, "L8"=8,"L9"=9,"L10"=10,"L11"=11)

parse_file <- function(file_path, type = 'train') {
  print(str_c(' > parsing', file_path, '... '))
  
  # get meta data
  meta_data <- read_lines(file_path, n_max = 10)
  path_vec <- str_split(file_path, '/', simplify = T)
  
  # getting site_id from file header, because that's how it is stored in the test set
  site_id <- meta_data[str_detect(meta_data, 'SiteID:')] %>%
    str_extract(., '^#\\tSiteID\\:(\\w+)') %>%
    str_sub(., str_locate(., ":")[1]+1, -1)
  
  
  if(type == 'train') {
    meta <- list(
      type = path_vec[3],
      floor_id = path_vec[6],
      floor_nr = floor_id_2_nr[[path_vec[6]]],
      site_id = site_id,
      file_id = path_vec[7]
    )
  } else {
    meta <- list(
      type = path_vec[3],
      floor_id = NULL,
      floor_nr = NULL,
      site_id = site_id,
      file_id = path_vec[4]
    )
  }
  
  # get the trace data 
  type_2_col_names <- list(
    "TYPE_WAYPOINT" = list(n_cols = 3, col_names = c('wy_x','wy_y'), chr_cols = NULL),
    "TYPE_GYROSCOPE" = list(n_cols = 5, col_names = c('tg_x','tg_y','tg_z','tg_a'), chr_cols = NULL),
    "TYPE_ACCELEROMETER" = list(n_cols = 5, col_names = c('acc_x','acc_y','acc_z','acc_a'), chr_cols = NULL),
    "TYPE_MAGNETIC_FIELD" = list(n_cols = 5, col_names = c('mf_x','mf_y','mf_z','mf_a'), chr_cols = NULL),
    "TYPE_ROTATION_VECTOR" = list(n_cols = 5, col_names = c('rv_x','rv_y','rv_z','rv_a'), chr_cols = NULL),
    "TYPE_ACCELEROMETER_UNCALIBRATED" = list(n_cols = 8, col_names = c('accu_x','accu_y','accu_z','accu_x2','accu_y2','accu_z2','accu_a'), chr_cols = NULL),
    "TYPE_GYROSCOPE_UNCALIBRATED" = list(n_cols = 8, col_names = c('gyru_x','gyru_y','gyru_z','gyru_x2','gyru_y2','gyru_z2','gyru_a'), chr_cols = NULL),
    "TYPE_MAGNETIC_FIELD_UNCALIBRATED" = list(n_cols = 8, col_names = c('mfu_x','mfu_y','mfu_z','mfu_x2','mfu_y2','mfu_z2','mfu_a'), chr_cols = NULL),
    "TYPE_WIFI" = list(n_cols = 6, col_names = c('wf_ssid','wf_bssid','wf_rssi','wf_freq','wf_lst'), chr_cols = c('wf_ssid','wf_bssid')),
    "TYPE_BEACON" = list(n_cols = 9, col_names = c('bea_uuid', 'bea_maj_id', 'bea_min_id', 'bea_tx', 'bea_rssi', 'bea_dist', 'bea_mac', 'bea_padding_time'),
                         chr_cols = c('bea_uuid', 'bea_mac', 'bea_maj_id', 'bea_min_id'))
  )
  
  process_type_data <- function(type_name, df) {
    df_type <- df[, 1:type_2_col_names[[type_name]]$n_cols]
    names(df_type) <- c('id', type_2_col_names[[type_name]]$col_names)
    
    if(is.null(type_2_col_names[[type_name]]$chr_cols)) {
      # change all columns to numeric
      df_type %<>%
        mutate_all(as.numeric)
    } else {
      # change all to numeric except chr_cols
      num_cols <- type_2_col_names[[type_name]]$col_names[!(type_2_col_names[[type_name]]$col_names %in% type_2_col_names[[type_name]]$chr_cols)]
      df_type %<>%
        mutate_at(num_cols, as.numeric)
    }
    
    return(df_type)
  }
  
  get_type <- function(df, type_name) {
    return(df %>% filter(V2 == type_name) %>% unnest(c(data)) %>% ungroup %>% select(-V2))
  }

  df <- read.csv2(file_path, sep="\t", skip=0, stringsAsFactors = FALSE, comment.char = "#", 
                header=FALSE, col.names = paste0("V", seq_len(10)))

  df_ty <- df %>%
    group_by(V2) %>%
    nest() %>%
    filter(V2 %in% names(type_2_col_names)) %>%
    transmute(V2, data = map2(.x = V2, .y = data, ~process_type_data(.x , .y)))
  
  #TODO: idsec in get_type func
  # way points
  wp <- get_type(df_ty, 'TYPE_WAYPOINT')
  if(nrow(wp) != 0) {
    wp %<>% mutate(idsec = round(id/1000))
  }
  
  # wifi data
  wifi <- get_type(df_ty, 'TYPE_WIFI')
  if(nrow(wifi) != 0) {
    wifi %<>% mutate(idsec = round(id/1000))
  }
  
  # beacon
  beacon <- get_type(df_ty, 'TYPE_BEACON')
  if(nrow(beacon) != 0) {
    beacon %<>% mutate(idsec = round(id/1000))
  }
  
  # device
  dd <- get_type(df_ty, 'TYPE_GYROSCOPE') %>%
    inner_join(get_type(df_ty, 'TYPE_ACCELEROMETER'), by='id') %>%
    inner_join(get_type(df_ty, 'TYPE_MAGNETIC_FIELD'), by='id') %>%
    inner_join(get_type(df_ty, 'TYPE_ROTATION_VECTOR'), by='id') %>%
    mutate(idsec = round(id/1000))
  
  return(list(
    meta = meta,
    wp = wp,
    device = dd, 
    wifi = wifi,
    beacon = beacon
  ))
  
}

tr_files <- list.files(path = dirs$train, recursive = TRUE, pattern = "\\.txt$", full.names = TRUE)
```

```{r, fig.width=15, fig.height=25}
# visualize paths
draw_traces_on_floor <- function(traces, site_id, floor_id, n_paths) {
  img <- readPNG(paste0(dirs$metadata, site_id, "/", floor_id, "/floor_image.png"))
  floor_info <- fromJSON(file = paste0(dirs$metadata, site_id, "/", floor_id, '/floor_info.json'))
  
  floor_image <- list(
    width  = dim(img)[1],
    height = dim(img)[2])
  
  floor_image$ratio_x <- floor_image$width/floor_info$map_info$width
  floor_image$ratio_y <- floor_image$height/floor_info$map_info$height
  
  trs <- tr_files[str_detect(tr_files, site_id) & str_detect(tr_files, floor_id)] 
  n_max <- length(trs)
  
  if(n_paths > n_max | n_paths == -1) {
    n_paths <- n_max
  }
  
  trs %<>%
    sample(., n_paths) %>%
    enframe() %>%
    mutate(wps = map(.x = value, ~parse_file(.x)$wp))
    
  trs_u <- trs %>%
    select(-value) %>%
    unnest(cols = c(wps)) %>%
    arrange(name, id) %>%
    mutate(x = wy_x * floor_image$ratio_x,
           y = wy_y * floor_image$ratio_y)
  
  p <- trs_u %>%
    ggplot() +
    annotation_raster(img, xmin = 0, xmax = floor_image$width, ymin = 0, ymax = floor_image$height) +
    # geom_point() +
    # geom_line() +
    geom_path(aes(x = x, y = y, colour = factor(name), group = factor(name))) +
    geom_point(aes(x = x, y = y, colour = factor(name), group = factor(name))) +
    scale_color_viridis(alpha = 1, begin = 0, end = 1, direction = 1, discrete = TRUE, option = "D") +
    theme_minimal() +
    theme(legend.position='none') +
    xlim(0, floor_image$width) +
    ylim(0, floor_image$height)
 
  return(p)
}

site_id <- '5a0546857ecc773753327266'
floor_vec <- c('B1', 'F1', 'F2', 'F3', 'F4')
n_paths <- 100
p <- list()

for(i in seq_along(floor_vec)) {
  p[[i]] <- draw_traces_on_floor(tr_files, site_id = site_id, floor_id = floor_vec[i], 100)
}

do.call(grid.arrange, c(p, ncol = 2))
```

??? :
* relationships between each sensor data, as well as sensors and waypoints
** wifi
** smartphone sensors
* relationship between sensors, waypoints and floor number

```{r}
# checking what sites are in train and test sets
# and whether there is any overlap

# te_files <- list.files(path = dirs$test, recursive = TRUE, pattern = "\\.txt$", full.names = TRUE)
# 
# df_tr <- tr_files %>%
#   enframe(name = NULL) %>%
#   mutate(path_chunks = str_split(value, '/')) %>%
#   mutate(site_id = map_chr(path_chunks, 5),
#          floor_id = map_chr(path_chunks, 6),
#          path_id = map_chr(path_chunks, 7)) %>%
#   mutate(path_id = str_trim(str_replace(path_id, '.txt', ''))) %>%
#   select(-path_chunks, -value)
# 
# df_te <- te_files %>%
#   enframe(name = NULL) %>%
#   mutate(meta = map(.x = value, ~parse_file(.x, 'test')$meta)) %>%
#   mutate(site_id = map_chr(meta, function(x) x$site_id),
#          path_id = map_chr(meta, function(x) x$file_id)) %>%
#   mutate(path_id = str_trim(str_replace(path_id, '.txt', ''))) %>%
#   select(-meta, -value)

# takes long to genereate these, so I save them jic
# write.csv(df_tr, './temp/train_data_meta.csv', row.names = FALSE)
# write.csv(df_te, './temp/test_data_meta.csv', row.names = FALSE)

df_tr_meta <- read_csv('./temp/train_data_meta.csv')
df_te_meta <- read_csv('./temp/test_data_meta.csv')

tr_sites_vec <- df_tr_meta %>%
  select(site_id) %>%
  unique() %>%
  pull()

te_sites_vec <- df_te_meta %>%
  select(site_id) %>%
  unique() %>%
  pull()
  
# df_te %>%
#   select(site_id) %>%
#   unique() %>%
#   mutate(is_in_tr = site_id %in% tr_sites_vec) %>%
#   count(is_in_tr)
```

Training set: 204 sites
Test set: 24 sites
All test sites are in training set
None of the paths are in the test set
Paths in test set don't contain waypoints and floors - dependent variables


Data exploration for a selected site
```{r}
# 5da1389e4db8ce0c98bd0547
site_id <- te_sites_vec[1]

custom_left_join <- function(x, y, by = 'idsec') {
  if('id' %in% names(x)) {
    x %<>% select(-id)
  }
  
  if('id' %in% names(y)) {
    y %<>% select(-id)
  }
  
  if(by %in% names(x) & by %in% names(y)) {
    return(left_join(x, y, by = 'idsec'))
  } else {
    return(x)
  }
}

# generate train set for selected site_id
df_site <- tr_files[str_detect(tr_files, site_id)] %>%
  # sample(., 5) %>%
  enframe() %>%
  mutate(path_nr = 1:n()) %>%
  mutate(data = map(.x = value, ~parse_file(.x))) %>%
  mutate(floor_nr = map_chr(data, function(x) x$meta$floor_nr),
         wp = map(data, function(x) x$wp),
         device = map(data, function(x) x$device),
         wifi = map(data, function(x) x$wifi),
         beacon = map(data, function(x) x$beacon)) %>%
  select(-data, -value) %>%
  mutate(merged = map2(.x = wp, .y = wifi, ~custom_left_join(.x, .y, by = 'idsec')),
         merged = map2(.x = merged, .y = device, ~custom_left_join(.x, .y, by = 'idsec')),
         merged = map2(.x = merged, .y = beacon, ~custom_left_join(.x, .y, by = 'idsec'))) %>%
  select(floor_nr, merged) %>%
  unnest(c('merged')) %>%
  mutate(floor_nr = as.integer(floor_nr))

# save the generated data
write_csv(df_site, str_c('./temp/site_', te_sites_vec[1], '.csv'))

df_site <- read_csv(str_c('./temp/site_', te_sites_vec[1], '.csv'), 
              col_types = cols(
                  .default = col_double(),
                  wf_ssid = col_character(),
                  wf_bssid = col_character(),
                  bea_uuid = col_character(),
                  bea_maj_id = col_character(),
                  bea_min_id = col_character(),
                  bea_mac = col_character(),
                  bea_tx = col_double(),
                  bea_rssi = col_double(),
                  bea_dist = col_double(),
                  bea_padding_time = col_double()
              ))

```

## Floor prediction

### Wifi features

Seems like the best guess choice to start
* ssid: service set identifier (network name); 654 unique networks in selected the building 
* bssid: basic service set identifier, the same WLAN, but different access points; 955 access points in the selected building 
* RSSI: received signal strength indicator (RSSI), measurement of the power present in a received radio signal
* frequency: 
  + the lower frequencies that are transmitted here can more easily penetrate solid objects
  + the higher frequency band makes up for its shorter range with much faster WiFi speeds


```{r}
df_fl <- df_site %>%
  select(floor_nr, idsec, starts_with('wy_'), starts_with('wf_'), starts_with('mf_')) %>%
  drop_na(floor_nr, starts_with('wf_')) %>%
  unique()

# 955 unique bssids
# how many bssids are on different floors (500 on just one)
df_fl %>%
  group_by(wf_bssid) %>%
  summarise(floor_counts = n_distinct(floor_nr)) %>%
  count(floor_counts)

# 
bssid <- df_fl %>%
  group_by(wf_bssid) %>%
  summarise(floor_counts = n_distinct(floor_nr)) %>%
  ungroup() %>%
  filter(floor_counts > 1) %>%
  select(wf_bssid) %>%
  pull() %>%
  sample(., 1)
  
fig <- df_fl %>%
  filter(wf_bssid == bssid) %>%
  plot_ly(., x = ~wy_x, y = ~wy_y, z = ~floor_nr, color = ~wf_rssi)

fig <- fig %>% add_markers()
fig <- fig %>% layout(scene = list(xaxis = list(title = 'x'),
                     yaxis = list(title = 'y'),
                     zaxis = list(title = 'Floor')))
fig




```

```{r}
# 
set.seed(717)

# xgboost
library(xgboost)

x_tr <- df_fl %>%
  select(-wf_ssid, -starts_with('wy_'), -wf_lst, -wf_freq, -idsec) %>%
  mutate(wf_bssid = as.factor(wf_bssid)) %>%
  unique()

y <- x_tr$floor_nr
x_tr %<>% select(-floor_nr)

var_fac <- select_if(x_tr, is.factor)
var_num <- select_if(x_tr, is.numeric)

##Dummy variables
dummy_fac <- fastDummies::dummy_cols(var_fac, remove_first_dummy = TRUE)
var_dummy <- dummy_fac %>% select(-wf_bssid)
 
x_tr <- cbind(var_dummy, var_num)
X <- xgb.DMatrix(data = as.matrix(x_tr), label = y)

#Training model
p <- list()

cv_xgb <- xgb.cv(p, X, p$nrounds, nfold = 10, print_every_n = 30, early_stopping_rounds = 100)


```










```{r}

# floor prediction:
# https://www.kaggle.com/oxzplvifi/indoor-kmeans-gbm-floor-prediction

# Use the hosts' GitHub scripts to generate a grid map of (floor,X,Y,rssi,magnetism) values from the "step detection" and "orientation detection" for training the models. The hosts' scripts are available @ https://github.com/location-competition/indoor-location-competition-20 Copyright (c) 2017-2020 XYZ10, Inc. https://dangwu.com/

# https://www.kaggle.com/hiro5299834/wifi-features-with-lightgbm-kfold/comments

# tips:
# https://www.kaggle.com/oxzplvifi/indoor-gbm-postprocessing-xy-prediction

```


